% ----------------------------------------------------------------------------------------
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% Modifications by:
% Jake Robinson-Lieberman (jake@jakerl.com)
% https://github.com/jakerl/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used, needs to
% be compiled with biber rather than bibtex.
% ----------------------------------------------------------------------------------------

% print option removes coloring in document 
\documentclass[print]{resume}

% Specify the bibliography file to include publications
\addbibresource{bibliography.bib} 

\usepackage[mmddyy]{datetime}

%%% BEGIN DOCUMENT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%-----------------------------------------------------------------------------------------
%--- HEADER ------------------------------------------------------------------------------
%-----------------------------------------------------------------------------------------
% {first name}{last name}{job title/field} 
\header{jake}{robinson-lieberman}{software engineer}

%--- BEGIN ASIDE -------------------------------------------------------------------------
% in the aside section, each new line forces a line break
% use '~' for empty lines
\begin{aside}
%-----------------------------------------------------------------------------------------
%--- CONTACT -----------------------------------------------------------------------------
%----------------------------------------------------------------------------------------- 
\section{contact}
\href{https://www.google.com/maps/place/904+Hinman+Ave,+Evanston,+IL+60202/}{904 Hinman Ave. \#2G\\ Evanston, Illinois 60202}
~
(847) 845-6974
\href{mailto:jake@jakerl.com}{jake@jakerl.com}
~
\href{http://www.jakerl.com}{jakerl.com}
%\href{https://github.com/jakerl}{github.com/jakerl}
%-----------------------------------------------------------------------------------------
%--- LANGUAGE ----------------------------------------------------------------------------
%-----------------------------------------------------------------------------------------
\section{language}
english - native
spanish - proficient
%-----------------------------------------------------------------------------------------
%--- DEVELOPMENT -------------------------------------------------------------------------
%-----------------------------------------------------------------------------------------
\section{development}
Objective-C
C, C++, Java
UNIX, Git
\LaTeX, HTML/CSS 
%-----------------------------------------------------------------------------------------
%--- CLASS PROJECTS ----------------------------------------------------------------------
%-----------------------------------------------------------------------------------------
\section{class projects} 
%--- UNIX/LINUX PROGRAMMING --------------------------------------------------------------
\textbf{UNIX/Linux Programming}
$\bullet$ Interpreter \& Compiler
$\bullet$ Client-Server Model
$\bullet$ Web Parser/Filter
~
%--- OPERATING SYSTEMS -------------------------------------------------------------------
\textbf{Operating Systems}
$\bullet$ UNIX Shell
$\bullet$ Job/CPU Scheduling Simulator
~
%--- ARTIFICIAL INTELLIGENCE -------------------------------------------------------------
\textbf{Artificial Intelligence}
$\bullet$ Slide Puzzle Solver
$\bullet$ Sudoku Solver 
$\bullet$ Reinforcement Learning Simulator
~
%--- COMPUTER SYSTEMS ENGINEERING --------------------------------------------------------
\textbf{Computer Systems Engineering}
$\bullet$ Graphical Circuit Simulator
~
%--- MULTIDISCIPLINARY DESIGN ------------------------------------------------------------
\textbf{Multidisciplinary Design}
$\bullet$ FPGA Client-Server Application
~
~
~
~
~
~
\today
%--- END ASIDE ---------------------------------------------------------------------------
\end{aside}

%-----------------------------------------------------------------------------------------
%--- EDUCATION SECTION -------------------------------------------------------------------
%-----------------------------------------------------------------------------------------
\section{education}
% --- BEGIN ENTRY LIST -------------------------------------------------------------------
\begin{entrylist}

%--- THE UNIVERSITY OF DAYTON ------------------------------------------------------------
\entry
{}
{The University of Dayton \thinfont\footnotesize\addfontfeature{Color=lightgray}- Dayton, Ohio}
{August 2011 - May 2015}		
{Computer Engineering - Bachelor of Science\\Computer Science - Minor}

%--- LOYOLA ACADEMY ----------------------------------------------------------------------
\entry
{}
{Loyola Academy \thinfont\footnotesize\addfontfeature{Color=lightgray}- Wilmette, Illinois}
{August 2007 - May 2011}
{}

% --- END ENTRY LIST ---------------------------------------------------------------------
\end{entrylist}

\vspace{-20pt} % reduces whitespace in-between sections

%-----------------------------------------------------------------------------------------
%---EXPERIENCE SECTION -------------------------------------------------------------------
%-----------------------------------------------------------------------------------------
\section{experience}
% --- BEGIN ENTRY LIST -------------------------------------------------------------------
\begin{entrylist}

%--- REVEEL - iOS DEVELOPER ----------------------------------------------------------
\entry
{}
{Reveel \thinfont\footnotesize\addfontfeature{Color=lightgray}- Chicago, Illinois}
{November 2015 - January 2016}
{
\emph{Contract iOS Developer}
\begin{itemize}
    \item Developed first release of location-aware application from the ground up alongside remote developer within one month. 
    \item Utilized MVC pattern using Model and View Controller classes with Storyboard and Xib files.  
    \item Built Manager singletons to call REST API, leveraging AFNetworking to make HTTP requests, Mantle to transform JSON responses into Model objects, and parametrized blocks to manage method results. 
    \item Created complex screens with UITableViews, each consisting of custom UITableViewCell Xibs.
    \item Handled server errors globally with user-facing messages by localizing server response strings.
\end{itemize} 
}

%--- STAND4 - COMMUNITY MANAGER ----------------------------------------------------------
\entry
{}
{Stand4 \thinfont\footnotesize\addfontfeature{Color=lightgray}- Boca Raton, Florida}
{May 2015 - August 2015}
{
\emph{Community Manager}
\begin{itemize}
    \item Increased user engagement and satisfaction by guiding product decisions alongside continuous, strategic communication with users.
    \item Filtered all user-facing messages and communications to ensure a unified company voice.  
    \item Improved app store optimization as much as 16 search ranks by identifying target keywords, writing a calculated app description, and successfully encouraging app store reviews.
    \item Organized user satisfaction campaigns including marketing collateral sent to users worldwide.
\end{itemize}
}

%--- MINEME ------------------------------------------------------------------------------
\entry
{}
{MineMe \thinfont\footnotesize\addfontfeature{Color=lightgray}- Boca Raton, Florida}
{July 2015 - August 2015}
{
\emph{Front-End iOS Developer}
\begin{itemize}
    \item Built front-end of iPad application that generates a Minecraft style face from a user's picture.
	\item Implemented camera functionality with AVFoundation and a repurposed custom Xib file.
\end{itemize}
}

%--- STAND4 - LEAD DEVELOPER -------------------------------------------------------------
\entry
{}
{Stand4 \thinfont\footnotesize\addfontfeature{Color=lightgray}- Boca Raton, Florida}
{May 2014 - August 2014}
{
\emph{Lead iOS Developer, Internship}
\begin{itemize}
    \item Developed iOS application that allowed users to create a profile, take in-app actions linked to nonprofit organizations, and post comments and pictures to a public stream.  
    \item Utilized Parse for database management and scalability, CocoaPods for dependency management, TestFlight for internal testing, and Git for source control.
\end{itemize}
}

% --- END ENTRY LIST ---------------------------------------------------------------------
\end{entrylist}

\vspace{-10pt} % reduces whitespace in-between sections

%-----------------------------------------------------------------------------------------
%---LEADERSHIP SECTION -------------------------------------------------------------------
%-----------------------------------------------------------------------------------------
\section{leadership}
% --- BEGIN ENTRY LIST -------------------------------------------------------------------
\begin{entrylist}

%--- FLYER INNOVATIONS -------------------------------------------------------------------
\entry
{}
{Flyer Innovations \thinfont\footnotesize\addfontfeature{Color=lightgray}- The University of Dayton}
{January 2014 - January 2015}
{
\emph{Chief of Operations} 
\begin{itemize}
    \item Managed and maintained internal structure of think-tank-esque student-run organization. 
    \item Established club's presence on campus with chariot races sponsored by Red Bull.
    \item Fostered entrepreneurial ideation through team-based activities and challenges.
\end{itemize}
}

%--- MEN'S CLUB VOLLEYBALL ---------------------------------------------------------------
\entry
{}
{Men's Club Volleyball \thinfont\footnotesize\addfontfeature{Color=lightgray}- The University of Dayton}
{June 2013 - June 2015}
{
\emph{President}
\begin{itemize}
    \item Oversaw logistics, budget, and coaching of club team nationally ranked in the top 25.
    \item Led team as floor captain to the club's first conference championship in over 10 years.
\end{itemize}
}

%--- WOMEN'S CLUB VOLLEYBALL -------------------------------------------------------------
\entry
{}
{Women's Club Volleyball \thinfont\footnotesize\addfontfeature{Color=lightgray}- The University of Dayton}
{September 2012 - June 2015}
{
\emph{Coach}
\begin{itemize}
    \item Directed practices and matches, teaching high-level skills and strategies in each position.
    \item Led team as coach to a 14th place finish at national tournament.
\end{itemize}
}

% --- END ENTRY LIST ---------------------------------------------------------------------
\end{entrylist}

%%% END DOCUMENT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}